Supplementary Material for _A Guide to Pre-processing High-Frequency Animal Tracking Data_

### 2021-09-10 supplement/05_calibration_data.Rmd
add fig sd nbs

>>>>

Compare number of receivers and SD and speed.

```{r}
data_nbs = data[, c("NBS", "SD", "speed_in", "VARX", "VARY")]
data_nbs = melt(
  data_nbs,
  id.vars = c("NBS")
)
```

```{r}
# plot heatmaps
fig_sd_nbs = 
  ggplot(data_nbs)+
  geom_jitter(
    aes(factor(NBS), SD, col = speed_in),
    size = 0.2,
    alpha = 0.4
  )+
  geom_hline(
    yintercept = 100,
    lty = 2, col = "grey"
  )+
  geom_vline(
    xintercept = 1.5,
    lty = 2, col = "grey"
  )+
  scale_colour_viridis_c(
    option = "G", direction = -1,
    limits = c(0, 20),
    na.value = "red"
  )+
  coord_cartesian(
    expand = F,
    xlim = c(0.5, 6),
    ylim = c(1, 1e3)
  )+
  scale_y_log10()+
  theme_classic()+
  theme(
    # panel.border = element_rect(
    #   colour = "black",
    #   fill = "NA"
    # ),
    legend.key.width = unit(2, "mm"),
    legend.key.height = unit(5, "mm"),
    legend.position = c(0.8, 0.85),
    legend.background = element_blank()
  )+
  # facet_wrap(~variable)+
  labs(
    colour = "Speed (m/s)",
    x = "# WATLAS receivers",
    y = "Positioning error (SD)"
  )

ggsave(
  fig_sd_nbs,
  filename = "supplement/figures/fig_sd_nbs.png",
  height = 5,
  width = 3
)
```
